


\textsc{Experience}


\begin{itemize}[left=1.3em, labelsep=0.2em, labelwidth=2em, align=parleft]
\item
  \textbf{INNOVACCER INC.} \hfill Noida, India \\
\noindent \emph{Senior Data Analyst}\hfill \emph{Aug `21 - Present}

    {\bfseries •} Data Solutions Architect implementing Analytics and Business
    Insights products, for large healthcare and insurance organizations
    as well as internal process improvement.

    {\bfseries •} Designed and maintained high-performance Power BI dashboards for healthcare organizations, improving operational insights and reducing decision-making time by 30\%.

    {\bfseries •} Developed and deployed machine learning models for time-series forecasting using SARIMA/Prophet, integrated with Power BI for real-time insights.

    {\bfseries •}Conducted advanced performance tuning on KustoQL for Power BI-based solutions. Leveraged Azure Synapse Analytics to design and implement data pipelines, enabling real-time data integration and analytics across cloud and on-premises sources, improving data processing efficiency in existing products by upto  50\%.

    {\bfseries •} Partnered with cross-functional teams to deliver scalable and accurate analytics solutions aligned with data governance requirements. Created internal tools, such as a JIRA-integrated dashboard, increasing SCRUM process efficiency by 80\%.

    {\bfseries •} Tech Stack: PowerBI, Python, SQL, KustoQL, MongoDB, Django, Azure, Figma, Git, JIRA, Microsoft Certified Azure Data Engineer (Pursuing).

\end{itemize}


\begin{itemize}[left=1.3em, labelsep=0.2em, labelwidth=2em, align=parleft]
\item
  \textbf{STAR-II AUTOMATED RURAL SOLAR PROJECT} 
  \hfill Indian Institute of Technology, Roorkee \\ 
  \noindent\emph{Undergraduate Project Intern \hfill \emph{Jun. `19 - Jul. `19}}

    {\bfseries •} Performed analytics on weather and sensor data from SCADA terminals to visualize and predict prototype efficiency under varying conditions.

    {\bfseries •} Joint Project under Dept. of Science and Technology, India and
    Province of Trento, Italy towards research on the viability of solar
    energy as an independently sustainable power source.
\\
\end{itemize}
